Investigating social change during cultural contact period using geometric morphometry of pottery shapes from Iron Age northeastern Taiwan

### 2019-12-23 analysis/paper/paper.Rmd
some questions about code

`Post-European` <- mshp$poe %T>% coo_plot(border="blue")
`Pre-European` <-  mshp$pre %T>% coo_plot(border="red", plot.new=FALSE)
`Chinese` <-       mshp$chi %T>% coo_plot(border="green", plot.new=FALSE)
legend("topright", 
       lwd=1,
       col=c("red", "blue", "green"), 
       legend=c( "Pre-European", "Post-European", "Chinese"))
```

@@

# Doesn't work if the plot is not produced by ggplot?
# plot_grid(a, b, labels = c('A', 'B'))

@@

```{r contribution-PCs, fig.cap= "Pottery shape variation based on scores along principal component axes. The rows from the top to the bottom represent the first to third principal component respectively. Each column shows the reconstructed shape variable according to the score mean ±2 standard deviation (SD) with a 0.5 interval"}
# the contributions of each PC to the shapes
pc_contrib <- PCcontrib(op.p, nax = 1:3) 
pc_contrib$gg +  
  geom_polygon(fill="slategrey", col="black") + 
  theme_minimal(base_size = 6)

@@

manv <- MANOVA_PW(op.p, "phase")
su_manv <- as.data.frame(manv$summary)

>>>>

`Post-European` <- mshp$poe %T>% coo_plot(border="blue")
`Pre-European` <-  mshp$pre %T>% coo_plot(border="red", plot.new=FALSE)
`Chinese` <-       mshp$chi %T>% coo_plot(border="green", plot.new=FALSE)
legend("topright", 
       lwd=1,
       col=c("red", "blue", "green"), 
       legend=c( "Pre-European", "Post-European", "Chinese")) 
#? How to put the legend out of the plot, tried change the margin using par(), but doesn't work
```

@@

#? How to plot them next to each other, cowplot doesn't work when the plot not ggplot objects?
# plot_grid(a, b, labels = c('A', 'B'))

@@

```{r contribution-PCs, fig.cap= "Pottery shape variation based on scores along principal component axes. The rows from the top to the bottom represent the first to third principal component respectively. Each column shows the reconstructed shape variable according to the score mean ±2 standard deviation (SD) with a 0.5 interval"}
# the contributions of each PC to the shapes
pc_contrib <- PCcontrib(op.p, nax = 1:3) 
#?How to hide above plot, tried dev.off but seems it only stop to compute the following one
pc_contrib$gg +  
  geom_polygon(fill="slategrey", col="black") + 
  theme_minimal(base_size = 6)

@@

manv <- MANOVA_PW(op.p, "phase") #? how to hide the process, echo = FALSE?
su_manv <- as.data.frame(manv$summary)
# how to reduce the number in the table to only 4 digits, tried mutate with signif but doesn't work?
#su_manv %>% 
  #mutate('Pr(>F)' = signif('Pr(>F)', 4))
